
\begin{acknowledgements}
\addchaptertocentry{\acknowledgementname} % Add the acknowledgements to the table of contents
 
 
In the name of Almighty \textbf{Allah}, the Most Gracious and the Most Merciful and the One, who gave me strengths and blessings to complete this master thesis. 

It had been a great honor and privilege to be a student of \textbf{Bauhaus University Weimar} with the financial support from DAAD that gave me the opportunity to peruse my masters degree among outstanding and professional people from the start of my studies until the end of my studies. I have learnt so many things that had never learnt before in my educational background. I write these acknowledgments to indicate the great people that my thesis would have not be completed without and I apologize to the ones that I forgot to state. 

I am indebted to my supervisor \textbf{Prof. Dr. Eva Hornecker}, who first accepted my thesis proposal, and guided me with her never-ending ideas that built the basis of this thesis. I am very inspired about her passion in HCI research and interdisciplinary projects that she has done and continuing to do. She has been always supportive and corporative whenever I was in need of help and advice.
I am equally grateful to my co-supervisor \textbf{Junior Professor Dr. Florian Echtler}, who supported the thesis technically by providing the mobile controller application and I appreciate his technical instructions and ideas on the use of body and mobile sensing technologies.
I would like to thank \textbf{Dipl.Ing.(FH) Patrick Tobias Fischer}, who in-depth monitored and assisted all my research methodologies and corrected my faults. He, with his strong experience and background in HCI, gave me outstanding ideas on advertisement design process, interaction methods and technical assistances in development stages. I thank him deeply for communicating with many officials for providing a convenient research field and space, which without his support I would have not been able to conduct my researches.

Very special thanks to \textbf{Thomas Apel} the coordinator of  \emph{Bauhaus-Walk} that accepted my request for making an advertisement for \emph{Bauhaus-Walk}. He and his group members were very supportive, kind and helpful in advertisement application design process and the materials. I also thank \textbf{Raika Nebelung} who is the project manager of university marketing that introduced me to \emph{Bauhaus-Walk} members, and talked to \textbf{Jens Braun}, who is the owner of \emph{Weimar tourist information center} to provide space for our research. I am heartily grateful from \textbf{Jens Braun} who had always a smile on his face and gave us space for more than four weeks for free, all of his employees were very kind and supportive I conducted my research in a very open and friendly environment. 

I thank to \textbf{Till Fastnacht} and \textbf{Daniel Pollack}, who were also working on their thesis in the same office with me. We always discussed on various issues and meanwhile brainstorming on creative ideas that helped me to think deeper. \textbf{Till fastnacht} tested my applications many times in lab and provided effective feedbacks and he also participated in my low-fi and high-fi prototype application demo videos. 

I am extremely delighted from my friends, who volunteered to help me in data gathering, as \textbf{Hamid Sabri} supported me in a four day data gathering in Mensa. My other dear and close friends like \textbf{Mohammad Asif Hoque, Shamsul Arefin, Kazi fakrul, Jetani Jenis, Ibrar Ahmed, Muhammad Umar Nawaz and Az Arezo }, who participated in depth-video analyzing which was an exhausted work and provided their feedback on application extreme testing scenarios. I thank \textbf{Xiangzhen Lü}, who artistically reshaped the theme of advertisement display and mobile interface and participated in various studies. \textbf{D.m. Masum} thank you for giving amazing ideas on application and for proof reading my thesis document beside other friends like \textbf{Zohra zekeria, Nana-Kesewaa Dankwa, Tayeba Abidi, Till, Ramin Ahadi and Mohib ameen} too who reviewed my thesis document

I want to thank my \textbf{Parents} who has always prayed for my success and gave me courage and hope for a better life and never let me knew about the hardship and problems they were facing in \textbf{Afghanistan} so that I could study with peaceful mind. I am so proud of my dear brother \textbf{Atiquallah Sahibzada} who has always uplift most responsibilities of family and struggled hard to create a better life, he was always been my role model in life. I send my peaceful prayer to my kind brother \textbf{Naqibullah Sahibzada} may his soul rest in peace, who was very happy when I started my masters, he was always passionate to do something big and was advising me to do too. I love you \textbf{Shafiullah Sahibzada} my cute brother whom I share love unlimitedly with.

And last but not least, I am very glad from my friend \textbf{Zohra Zekeria}, who has always stood beside me and gave me encouragements and hopes in difficult times and as a result I have achieved so many things that I could have not imagined to do in the past years. 


\end{acknowledgements}
