% Chapte 8 
\chapter{Interactive and non Interactive on site study} % Main chapter title

\label{Chapter8} % For referencing the chapter elsewhere, use \ref{Chapter1} 

\section{Introduction}

The On-sight study is going to be executed in Weimar tourist Information Center at (Weimar Markt 10) which is one of important location for many tourists who visit Weimar. This location was chosen by Bauhaus-Spaziergang program that are providing tours for new visitors in Weimar. Bauhaus-Spaziergang does advertisement as brochure at this location. The location is reserved for our new interactive advertisement starting from 1st February for three coming weeks. 

Two different Interactions and one non-Interactive Advertisement are made. The first one is body interaction where passers-by can interact using their body movement in the physical space and influence advertisement element in the screen. The second is mobile interaction where users by opening the advertisement web application in their smartphone, can interact with advertisement and the third is a non-interactive advertisement where the interface and elements are completely similar but are not influence by people around, they change based on time-based random sequence. 

\section{Interactive Advertisement}

\section{Auto Interactive Advertisement}
?
\section{Problem Statement}
\begin{enumerate}

\item	For which of the three conditions (body, mobile and non-interactive advertisements) passers-by 

\begin{enumerate}
\item	Are more attracted toward.
\item	Perform of Honeypot and Landing effects.
\item	Are engaged with the screen.
\item	Spend extra time for watching the remaining advertisement after interaction.
\end{enumerate}

\item Find out potential conversion rate toward the Bauhaus-Walk program.
\item	How many people understand advertisement?
\item	Get general opinion about the advertisement techniques.
\item	Comparison of Mobile and body interaction techniques.

\end{enumerate}






\section{Design study}






\section{Data gathering}
I would like to gather as much data as I can from different aspects on-sight so that I could be on safe side and if any possible question would arise after the experiment the gathered data should be able to answer that too. Based on the above-mentioned possible questions, I would perform the bellow data-gathering techniques.

\begin{enumerate}
\item On-Site Observation:
Two different timings during the day, mornings and evenings each for two hours will be observed. The goal of observation is to count number of glances and do note taking of landing, honeypot effects and other interesting behaviors. 
 
\item System Logs
The Interactive advertisement application can generate logs for both mobile and body.
\begin{enumerate}
\item	Mobile Interaction.
\begin{itemize}
\item	Time user joins.
\item	Interaction completion time.
\item	Number of elements (locations) explored.
\item	Whole duration the user was.
\item	If the user has seen advertisement or not.
\end{itemize}
\item	Body Interaction.
\begin{itemize}
\item	Time user joins.
\item	Interaction completion time.
\item	Number of elements (locations) explored.
\item	Whole duration the user was.
\item	If the user has seen advertisement or not.
\end{itemize}

\end{enumerate}
\end{enumerate}



















